WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-09-15 ms.tex
Single column-wide figure

In the frequency domain, the strain observed by a single \ac{GW} interferometer is
%
\begin{equation}\label{eq:signal-model}
    y_i (\omega) = x_i (\omega; \bm\theta) + n_i (\omega),
\end{equation}
%
where $x_i (\omega; \bm\theta)$ is the \ac{GW} signal given a parameter vector $\bm\theta$ that describes the \ac{GW} source, and $n_i (\omega)$ is that detector's \ac{WSS} Gaussian noise with one\nobreakdashes-sided \ac{PSD} $S_i(\omega) = E\left[\left|n_i(\omega)\right|^2\right] + E\left[\left|n_i(-\omega)\right|^2\right] = 2 E\left[\left|n_i(\omega)\right|^2\right]$. We shall denote the combined observation from a network of detectors as $\mathbf y (\omega) \equiv \{y_i (\omega)\}_i$.

The likelihood, or the probability of obtaining the observation $\mathbf y$ conditioned on the value of $\bm\theta$, is a product of Gaussian distributions:
%
\begin{multline}\label{eq:gaussian-likelihood}
    \mathcal{L}(\mathbf y; \bm\theta) = \prod_i p(y_i | \bm\theta)
        \\ \propto \exp \left[
        - \frac{1}{2} \sum_i \int_0^\infty \frac{\left|y_i (\omega)
            - x_i(\omega; \bm\theta) \right|^2}{S_i(\omega)} \, d\omega
    \right].
\end{multline}

@@

\begin{figure}
    \begin{center}
        \includegraphics{crlb_tau}

        \includegraphics{crlb_gamma}
    \end{center}
    \caption{\label{fig:crlb-tau}\ac{CRLB} on root\nobreakdashes-mean square timing uncertainty, using the likelihood for the full GW data (Equation~\ref{eq:gaussian-likelihood-spa}; dashed diagonal line) or the autocorrelation likelihood (Equation~\ref{eq:autocor-likelihood}; solid lines) with a selection of arrival time priors.}
\end{figure}

>>>>

In the frequency domain, the strain observed by a single \ac{GW} interferometer is
%
\begin{equation}\label{eq:signal-model}
    y_i (\omega) = x_i (\omega; \bm\theta) + n_i (\omega),
\end{equation}
%
where $x_i (\omega; \bm\theta)$ is the \ac{GW} signal given a parameter vector $\bm\theta$ that describes the \ac{GW} source, and $n_i (\omega)$ is that detector's Gaussian noise with one\nobreakdashes-sided \ac{PSD} $S_i(\omega) = E\left[\left|n_i(\omega)\right|^2\right] + E\left[\left|n_i(-\omega)\right|^2\right] = 2 E\left[\left|n_i(\omega)\right|^2\right]$. We shall denote the combined observation from a network of detectors as $\mathbf y (\omega) \equiv \{y_i (\omega)\}_i$.

The likelihood, or the probability of the observation $\mathbf y$ conditioned on the value of $\bm\theta$, is a product of Gaussian distributions:
%
\begin{multline}\label{eq:gaussian-likelihood}
    \mathcal{L}(\mathbf y; \bm\theta) = \prod_i p(y_i | \bm\theta)
        \\ \propto \exp \left[
        - \frac{1}{2} \sum_i \int_0^\infty \frac{\left|y_i (\omega)
            - x_i(\omega; \bm\theta) \right|^2}{S_i(\omega)} \, d\omega
    \right].
\end{multline}

@@

\begin{figure*}
    \begin{center}
        \includegraphics{crlb_tau}
        \includegraphics{crlb_gamma}
    \end{center}
    \caption{\label{fig:crlb-tau}\ac{CRLB} on root\nobreakdashes-mean square timing uncertainty, using the likelihood for the full GW data (Equation~\ref{eq:gaussian-likelihood-spa}; dashed diagonal line) or the autocorrelation likelihood (Equation~\ref{eq:autocor-likelihood}; solid lines) with a selection of arrival time priors.}
\end{figure*}
